\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\title{ADA Summary: Week 1 Jan 17-23}
\author{Peem Lerdputtipongporn}
\date{$20^{th}$ January 2022}

\begin{document}

\maketitle

Below are what I have done during Week 1 of the ADA project.

\section{What I have done}

\begin{itemize}
    \item Update basic libraries (e.g., Pandas, numpy, matplotlib) and ensure
    they can be used on my Jupyter notebook.
    \item Create Github repository with initial dataset.
    \item Perform EDA on each variable and jot down questions I have.
    Overall, the variables are self-explanatory
    but there are some weird inputs (see Jupyter notebook)
    \item Compile a list of questions about the dataset to send to our external collaborators
    (expected to send by Thursday evening).
\end{itemize}

\section{Updates on last week's plan}

Not applicable.

\section{Plans for next week}

\begin{itemize}
  \item Read two of Rema's papers on video classification
  as well as initial-meeting notes. Identify the project's motivation,
  dataset, analysis methods, results, and future extensions and jot them down
  (Deadline: before we meet)
  \item Refresh myself on basic data manipulation with pandas, numpy, sklearn
  (Ongoing).
  \item Perform EDA on other variables. Compile any surprising results to bring up
  to our collaborators (Ongoing).
\end{itemize}

\section{Questions to discuss when we meet}
\begin{itemize}
  \item Python or R? What should I spend time becoming more fluent in.
  It has been a while since I last used Python, so I'm having some difficulty with EDA,
  especially how to visualize the dataset. The dataset is also quite messy.
  \item Set up expectations and regular meeting time and frequency.
  How should I update you on my progress? When should I contact you (also how) if
  I encounter problems I cannot resolve.
  \item When to schedule a meeting with Rema and her colleagues (i.e., until which point
  have we made enough progress to contact them)? Source code for previous projects
  they did on this dataset.
  \item Larry?
\end{itemize}

\end{document}
